NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-08-10 ms_nihao_budget.tex
add one paragraph to show the convergence of our result.

%% FIGURE 2
\begin{figure}
\centerline{
  \psfig{figure=budget_res.eps,width=0.48\textwidth}
}
\caption{Linear fractional baryon content of our NIHAO simulations  as a
  function of halo mass. }
\label{fig:budget_res}
\end{figure}

@@

>>>>

%% FIGURE 2
\begin{figure}
\centerline{
  \psfig{figure=budget_res.eps,width=0.48\textwidth}
}
\caption{{\bf Linear fractional baryon content of our NIHAO simulations  as a
  function of halo mass color coded by number of all particles per halo.}}
\label{fig:budget_res}
\end{figure}

@@

{\bf Since the resolution is one key parameter in simulation, 
the convergence of the baryonic fraction predicted by NIHAO suite
is worth to estimate. Fig.~\ref{fig:budget_res} shows baryonic 
fraction color coded by number of total particles per halo.
In the plot, the number of total partilce per halo spans 2 magnitudes
and has no correlation with baryonic fraction. Therefore, we can conclude 
the resolution of NIHAO suite is proper to study the fractional 
baryon content.}
